### 2014-06-12 alex/initial.Rmd
found out student ids are not unique

>>>>

Let's see if parent income has any effect on student performance
```{r parents, cache=TRUE}
library(ggvis)
students = student2012 %>% select(CNT, STIDSTD, math, read, sci)
parents = parent2012 %>% select(CNT, STIDSTD, PA07Q01,
                                PA03Q01, PA03Q02, PA03Q03, PA03Q04,
                                PA05Q01, PA05Q02, PA05Q03, PA05Q04)
student_parent = students %>% left_join(parents, by = "STIDSTD") %>% filter(!is.na(PA07Q01)) %>% arrange(desc(math))
head(student_parent, 50)
```

Apparently student IDs are not unique!  Students from different countries can share IDs.
